Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2023-11-21 lqg-strings.tex
Just changed wording after eq(42)
added new calculations to main file

Following the usual procedure such as the one found in \cite{Tong2009Lectures}, we find two copies of the string energy-momentum tensor being set to zero, which can be used to find an expression for the induced metrics:
\begin{equation} \label{eqn:variation-wrt-g}
	\frac{\delta S_{P B}}{\delta g^{c d}} \overset{!}{=} 0
\end{equation}
\begin{equation*}
	\downarrow
\end{equation*}
\begin{multline} \label{eqn:g-em-tensor}
	T^{(G)} _{c d} := G_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\nu} - \\
	- \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = 0
\end{multline}
\begin{equation*}
	\Downarrow
\end{equation*}
\begin{equation} \label{eqn:g-expression}
	g_{c d} = 2 f^{(G)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} ,
\end{equation}
where the function $f^{(G)}$ is given by
\begin{equation} \label{eqn:g's-f-function}
	\frac{1}{f^{(G)}} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu},
\end{equation}
and completely analogously for the $H_{\mu \nu}$ metric,
\begin{equation} \label{eqn:variation-wrt-h}
	\frac{\delta S_{P B}}{\delta h^{c d}} \overset{!}{=} 0
\end{equation}
\begin{equation*}
	\downarrow
\end{equation*}
\begin{multline} \label{eqn:h-em-tensor}
	T^{(H)} _{c d} := H_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\mu} - \\
	- \frac{1}{2} h_{c d} h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = 0
\end{multline}
\begin{equation*}
	\Downarrow
\end{equation*}
\begin{equation} \label{eqn:h-expression}
	h_{c d} = 2 f^{(H)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} H_{\mu \nu} ,
\end{equation}
with
\begin{equation} \label{eqn:h's-f-function}
	\frac{1}{f^{(H)}} = h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} H_{\mu \nu} .
\end{equation}

As for the embbeding fields equation, we get a wave equation for the coupled metric
\begin{equation} \label{eqn:variation-wrt-X}
	\frac{\delta S_{P B}}{\delta X^{\lambda}} \overset{!}{=} 0
\end{equation}
\begin{equation*}
	\downarrow
\end{equation*}
\begin{equation} \label{eqn:bimetric-wave-equation}
	f^{\prime a b} \partial _{a} \partial _{b} X^{\mu} F_{\mu \lambda} = \frac{1}{2} f^{\prime a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \frac{\partial F_{\mu \nu}}{\partial X^{\lambda}} ,
\end{equation}
where
\begin{equation} \label{eqn:coupled-ws-metric}
	f^{\prime a b} & = T \sqrt{- g} g^{a b} + T' \sqrt{- h} h^{a b}
\end{equation}
\begin{equation} \label{eqn:combined-bulk-metric}
	F_{\mu \nu}    & = G_{\mu \nu} + H_{\mu \nu} ,
\end{equation}
in which we add a prime in the coupled metric $f^{\prime a b}$ since it is not quite the metric induced by the combined bulk metric $F_{\mu \nu}$. Since 2D metrics can always be written as a conformal metric, it is easy to see that eq(\ref{eqn:coupled-ws-metric}) can be recast as
\begin{equation} \label{eqn:conformal-coupled-metric}
	f^{\prime a b} = T \eta ^{a b} + T' \eta ^{a b} = (T + T') \eta ^{a b} ,
\end{equation}
and in the special case of the second metric coming from the quantum geometry inverse area correction where $T' = T g \Delta / 2$ and the background geometry being fixed i.e $\partial _{\lambda} F_{\mu \nu}$, we see that eq(\ref{eqn:bimetric-wave-equation}) almost reduces to eq(\ref{eqn:simplified-modified-wave-eqn}), the only difference being that the correction factor loses the dependence on the determinant $h$.

>>>>

Following the usual procedure such as the one found in \cite{Tong2009Lectures} with the bulk metric fixed, we find two copies of the string energy-momentum tensor being set to zero, which can be used to find an expression for the induced metrics:
\begin{equation} \label{eqn:variation-wrt-g}
	\frac{\delta S_{P B}}{\delta g^{c d}} \overset{!}{=} 0
\end{equation}
\begin{equation*}
	\downarrow
\end{equation*}
\begin{multline} \label{eqn:g-em-tensor}
	T^{(G)} _{c d} := G_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\nu} - \\
	- \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = 0
\end{multline}
\begin{equation*}
	\Downarrow
\end{equation*}
\begin{equation} \label{eqn:g-expression}
	g_{c d} = 2 f^{(G)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} ,
\end{equation}
where the function $f^{(G)}$ is given by
\begin{equation} \label{eqn:g's-f-function}
	\frac{1}{f^{(G)}} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu},
\end{equation}
and completely analogously for the $H_{\mu \nu}$ metric,
\begin{equation} \label{eqn:variation-wrt-h}
	\frac{\delta S_{P B}}{\delta h^{c d}} \overset{!}{=} 0
\end{equation}
\begin{equation*}
	\downarrow
\end{equation*}
\begin{multline} \label{eqn:h-em-tensor}
	T^{(H)} _{c d} := H_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\mu} - \\
	- \frac{1}{2} h_{c d} h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = 0
\end{multline}
\begin{equation*}
	\Downarrow
\end{equation*}
\begin{equation} \label{eqn:h-expression}
	h_{c d} = 2 f^{(H)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} H_{\mu \nu} ,
\end{equation}
with
\begin{equation} \label{eqn:h's-f-function}
	\frac{1}{f^{(H)}} = h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} H_{\mu \nu} .
\end{equation}

As for the embbeding fields equation, we get a non-homogeneous wave equation for the coupled metric
\begin{equation} \label{eqn:variation-wrt-X}
	\frac{\delta S_{P B}}{\delta X^{\lambda}} \overset{!}{=} 0
\end{equation}
\begin{equation*}
	\downarrow
\end{equation*}
\begin{equation} \label{eqn:bimetric-wave-equation}
	\partial _{a} \left( f^{\prime a b} \partial _{b} X^{\mu} \right) F_{\mu \lambda} = 0 ,
\end{equation}
with the coupled metric $f^{\prime a b}$ and the combined bulk metric $F_{\mu \nu}$ given by
\begin{equation} \label{eqn:coupled-ws-metric}
	f^{\prime a b} = T \sqrt{- g} g^{a b} + T' \sqrt{- h} h^{a b}
\end{equation}
\begin{equation} \label{eqn:combined-bulk-metric}
	F_{\mu \nu} = G_{\mu \nu} + H_{\mu \nu},
\end{equation}
where the coupled metric $f^{\prime a b}$ has a prime since it is not quite the metric induced by the combined metric $F_{\mu \nu}$. In the special case where $h = g^{-1}$ and $T' = T k \Delta / 2$, we get
\begin{multline} \label{eqn:h-equal-g-inverse-f'}
	f^{\prime a b} = T \bigg( \sqrt{- g} g^{a b} + \\
	+ \frac{k \Delta}{2} \sqrt{- g^{-1}} U^{a} _{\ a'} (g^{-1})^{a' b'} U^{\ b} _{b'} \bigg) ,
\end{multline}
where we have a new $\mathrm{SO}(1,1)$ symmetry in the second metric since forcing the determinant to be the inverse of the first doesn't mean the second matrix will be just the inverse, but rather any matrix that differs by an orthogonal transformation $U$. Given the metric itself is a function of world-sheet coordinates, we require this to be a local symmetry $U(x)$, thus eq(\ref{eqn:bimetric-wave-equation}) becomes
\begin{multline} \label{eqn:gauge-wave-eqn}
	f^{\prime a b} \partial _{a} \partial _{b} X^{\mu} + T \Big( \partial _{a} (\sqrt{- g} g^{a b}) + \\
	+ \frac{k \Delta}{2} \Big( U^{a} _{\ a'} \partial _{a} (\sqrt{- g^{-1}} (g^{-1})^{a' b'}) U^{\ b} _{b'} + \\
	+ \partial _{a} U^{a} _{\ a'} (\sqrt{- g^{-1}} (g^{-1})^{a' b'}) U^{\ b} _{b'} + \\
	+ U^{a} _{\ a'} (\sqrt{- g^{-1}} (g^{-1})^{a' b'}) \partial _{a} U^{\ b} _{b'} \Big) \Big) \partial _{b} X^{\mu} = 0 ,
\end{multline}
and after applying the conformal symmetry of 2D metrics in the form $g^{a b} = (\phi (x))^{-1} \eta ^{a b}$ the above equation reduces to
\begin{multline}
	\left( 1 + \frac{k \Delta}{2} \right) \eta ^{a b} \partial _{a} \partial _{b} X^{\mu} + \\
	+ \frac{k \Delta}{2} \Big( \partial _{a} U^{a} _{\ a'} \eta ^{a' b'} U^{\ b} _{b'} + \\
	+ U^{a} _{\ a'} \eta ^{a' b'} \partial _{a} U^{\ b} _{b'} \Big) \partial _{b} X^{\mu} = 0 .
\end{multline}
